%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevSecOps Chapter Lead} % Job title
    {Devo} % Organization
    {Madrid, Spain} % Location
    {Aug. 2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Secure SDLC toolchain design and implementation.}
        \item {Lead POCs with different providers looking for best fit security solutions.}
        \item {Design, integrate and automation of security processes, most of times by Gitlab-ci.}
        \item {Manage and admin different security tools and services like Sonarqube or Snyk.}
        \item {Improve best security practises around development and architecture.}
        \item {Advodcate in vulnerability management, triage and mitigations.}
        \item {Cooperation with CISO team translating requirements, getting and integrating them.}
        \item {Identification of security needs with bussiness.}
        \item {Take part of Fedramp ceertification, compliance and requirements.}
        \item {Implementation of security controls.}
        \item {TechStack keywords: AWS, Gitlab, Terragrunt, Helm, EKS, SAST, SCA, Snyk, Sonarqube, Burp, Tenable.io, Tenable.cs. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Cyber Security Team} % Job title
    {PagoNxt} % Organization
    {Madrid, Spain} % Location
    {Oct. 2020 - Aug. 2021} % Date(s)
    {
     \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assumtion SecDevOps role taks into eCISO team.}
        \item {Plan, revise and deploy DevOps Security.}
        \item {Automate security processes.}
        \item {Work in Day-to-day translating CISO security controls to the entity.}
        \item {Azure: Desing and implementation: Monitoring, policies.}
        \item {Take part of the architecture designs, leading different POCs about PAM or policy controlers.}
        \item {Colaborate with different stakeholders like ALM team, or different subEntities like SuperDigital Brasil to improve security processes and desings.}
        \item {TechStack keywords: Azure, Azure Policies Github ,Terraform, Terragrunt, EKS, VmSS, Ansible }
    \end{cvitems}
    }

%---------------------------------------------------------
    \cventry
    {Cloud Architect} % Job title
    {Prefapp} % Organization
    {Santiago de Compostela, Spain} % Location
    {Oct.2019-Aug.2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project: Migration on premise Moodle Elearning Platform to Azure (University Santiago de Compostela USC) }
        \item {Migration on premise Moodle Elearning Platform to Azure. IaC by Azure Resource manager.-ARM-}
        \item {Deployment, monitoring, backup, log system and services involved in the platform. HA}
        \item {Azure Monitor, Application Insigts, Log Analytics and Grafana. Packer, Ansible, Azure Devops}
        \item {Project: Decouplep monolith (Tecalis)}
        \item {Decoupled API, implement CI-CD pipelines over Gitlab with CloudRun as infrastructure.}
        \item {Google Cloud Services, Cloud Run, IAM, Docker Registry, Docker, PHP, Laravel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {BI Cloud Administrator} % Job title
    {Vector-ITC} % Organization
    {Madrid, Spain} % Location
    {2018-2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project: Data Office (Inditex)}
        \item {Systems team over BI department.}
        \item {Database performance tests.}
        \item {Analisys of solutions, requirements, architecture, hardware, security for the integration of new BI solutions. Exasol firts level manage.}
        \item {Processes monitoriing: ETL, OLAP cubes. Support for integrate BI solutions: Tableau ,Exasol,Hadoop.}
        \item {Project: Glow, Big data project (Meliá Hotels)}
        \item {Managing, operation, data flow analysis, improving and debugging ETL processes on a full big data architecture.}
        \item {Redhat administration over EC2 AWS, Install, configuration, deployments, updates and hardening  services.}
        \item {Operations: deployments, service and functional monitoring, versioning.}
        \item {Management and user support.}
        \item {Continuous delivery: Jenkins, Codecommit, Jira.}
        \item {AWS: Redshift, RDS ,EC2 ,ETL, Tomcat, Pentaho, MicroStrategy}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Architect} % Job title
    {Plexus Technologies} % Organization
    {Santiago de Compostela, Spain} % Location
    {2015-2018} % Date(s) 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Project: Sun Identity management migration to openIdm ( SESPA: public health service)}
        \item {Analysis of the bussines logic, architecture and requirements, test planning, deployment and monitorization.}
        \item {Manage bussines roles and bussines logic.}
        \item {Technologies:Openidm, Galera Cluster , openLDAP Cluster, Java ICF, connectors, MS AD, Oracle , SQLServer, SPML, Python, YAML , Centos 7, Novell Metadirectory.}
        \item {Project: WifiPlex. (Plexus product development)}
        \item {NAC.Hardware solution for access control and management of user connectivity in large areas based on RouterOS. Network electronics and ARM board}
        \item {FreeRadius,Nginx MySQL, embedded systems, physical and logical security: network, services.}
        \item {Integration with PayPal, PMS, self-registration, social networks, bandwidth control, line balancing, failover}
        \item {Migration the solution to a cloud integration to Wifiplex Cloud: Roadming and centralized management.}
        \item {Technologies: Aruba Instant , Mikrotik, Cisco, Vmware , Fedora ,Centos ,Redhat.} 
    \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Linux Support} % Job title
    {Dinahosting S.L.} % Organization
    {Santiago de Compostela, Spain} % Location
    {Jul 2014-Aug 2015 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Linux tech support, hosting services.Wordpress and other CMS.}
        \item {Services Apache ,MTA ,FTP , MySQL , DNS. Domain manage.}
        \item {Physical server and VPS monitoring under XEN}
        \item {Malware incident response and prevention.}
    \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Network facilities manager} % Job title
    {Bosh Sec Systems} % Organization
    {Vigo, Spain} % Location
    {Jan 2006 -Jul 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Voice and VoIP and data services integration TELE2/Vodafone over xDSL, documentation, technical and administrative}
       \item {Technical and administrative support. Remedy, Clarify, Metasolv.}
       \item {Provision of voice and data equipment. Diagnosis and resolution of voice, voIP and data faults.}
       \item {Coordination and verification of technicians onhouse and OBA.Administrative and technical help on remote to field technicians.}
       \item {Cisco Network Register Alcatel Network Analyzer. Alcatel DSLAM GSM y Femtocells.Equipos Cisco, Huawei, Oneaccess.} 
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Technical Support} % Job title
    {Novo Milenio systems} % Organization
    {Ourense, Spain} % Location
    {2002-2003} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Management of incidents. SAT to SMEs at the physical and logical level. Microinformatics, peripherals.}
        \item {Configuration, installation and maintenance of Dell and IBM Neftinity 5000 and 5500 series servers by implementing}
        \item { Windows 2000 and Mail, DNS, FTP, HTTP Services}
      \end{cvitems}
    }

\end{cventries}
